### 2009-08-25 doc/tutorials/ws-programming-tutorial/doc/tex_appendix/appendix.tex
Update schema locations in tutorial document

\lstsetJUSTXML
\lstinputlisting
	[
	label=lst:mcc.xsd,
	caption={[XML schema of configuration files.]\textbf{XML schema of configuration files.}}
	]{../../../../src/hed/libs/loader/mcc.xsd}

\lstsetJUSTXML
\lstinputlisting
	[
	label=lst:tcp.xsd,
	caption={[XML schema of the TCP component.]\textbf{XML schema of the TCP component.}}
	]{../../../../src/hed/mcc/tcp/tcp.xsd}

\lstsetJUSTXML
\lstinputlisting
	[
	label=lst:tls.xssd,
	caption={[XML schema of the TLS component.]\textbf{XML schema of  the TLS component.}}
	]{../../../../src/hed/mcc/tls/tls.xsd}

\lstsetJUSTXML
\lstinputlisting
	[
	label=lst:http_xsd,
	caption={[XML schema of the HTTP component.]\textbf{XML schema of the HTTP component.}}
	]{../../../../src/hed/mcc/http/http.xsd}

>>>>

\lstsetJUSTXML
\lstinputlisting
	[
	label=lst:mcc.xsd,
	caption={[XML schema of configuration files.]\textbf{XML schema of configuration files.}}
	]{../../../../src/hed/libs/loader/schema/loader.xsd}

\lstsetJUSTXML
\lstinputlisting
	[
	label=lst:tcp.xsd,
	caption={[XML schema of the TCP component.]\textbf{XML schema of the TCP component.}}
	]{../../../../src/hed/mcc/tcp/schema/tcp.xsd}

\lstsetJUSTXML
\lstinputlisting
	[
	label=lst:tls.xssd,
	caption={[XML schema of the TLS component.]\textbf{XML schema of  the TLS component.}}
	]{../../../../src/hed/mcc/tls/schema/tls.xsd}

\lstsetJUSTXML
\lstinputlisting
	[
	label=lst:http_xsd,
	caption={[XML schema of the HTTP component.]\textbf{XML schema of the HTTP component.}}
	]{../../../../src/hed/mcc/http/schema/http.xsd}
